14th International Satisfiability Modulo Theories Competition (SMT-COMP 2019): Rules and Procedures

### 2019-04-19 rules/rules19.tex
Rules: Pass over Single Query Track.

The \maintrack competition will consist of selected benchmarks in each
of the logic divisions.  Each benchmark script will be presented to
the solver as its first command-line argument.  The solver is then
expected to attempt to report on its standard output channel whether
the formula is satisfiable (\texttt{sat}, in lowercase) or
unsatisfiable (\texttt{unsat}).  A solver may also report
\texttt{unknown} to indicate that it cannot determine satisfiability
of the formula.

The \maintrack competition uses a StarExec post-processor (named
``SMT-COMP 2019") to accumulate the results.

>>>>

\header{Input/Output.}
This track will consist of selected non-incremental benchmarks in each of
the logic divisions.  Each benchmark will be presented to the solver as its
first command-line argument.  The solver is then expected to report on its
standard output channel whether the formula is satisfiable (\texttt{sat}) or
unsatisfiable (\texttt{unsat}).  A solver may also report \texttt{unknown} to
indicate that it cannot determine satisfiability of the formula.

\header{Time Limit.}
This track will use a wall-clock time limit of 40 minutes per solver/benchmark
pair.

\header{Postprocessor.}
This track uses a StarExec post-processor (named \rem{tba}) to accumulate the
results.
